---
title: "Psycorona - Data Cleaning Documentation"
subtitle: "Step by step description" 
author: "PsyCorona Gang"
date: "3/30/2020"
output:
  html_document: 
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
editor_options:
  chunk_output_type: console
---


<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>


```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  rm(list=ls()) # clear workspace
  gc # garbage collector
  
# Install and Load Packages
  #if(!require(pacman)) install.packages("pacman")
  # require(pacman)
  # pacman::p_load(psych, ggplot2, ggthemes, haven, data.table, dplyr, tidyr, Hmisc, mada, 
  #                knitr, kableExtra, naniar, stats, readxl, matrixStats, ISOcodes, pander,
  #                Scale)
lib <- c("psych", "ggplot2", "ggthemes", "haven", "data.table", "dplyr", "tidyr", "Hmisc", "mada", 
         "knitr", "kableExtra", "naniar", "stats", "readxl", "matrixStats", "ISOcodes", "pander", "Scale")

invisible(lapply(lib, library, character.only = TRUE))  
lapply(lib, library, character.only = TRUE)
  
# Load Custom Packages  
  source("./scripts/functions/fun.panel.R")
  source("./scripts/functions/themes.R")
  source("./scripts/functions/dictionary_functions.R")
  
# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(echo = TRUE)
```

Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.   

<br/>

## **Import Data**
In a first step we import the raw Qualtrics data, which was downloaded as an SPSS file.   

```{r LoadRaw, echo=T, warning=F, message=F}
# Reset working directory to folder current file is saved in
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# Import Qualtrics Survey Data
dt0RawRUG <- read_spss("data/raw data/Snowball+Corona+Long-Term+Coverage+-+Baseline_April+2,+2020_08.59.sav")
dt0RawRUG$source <- "RUG"

dt0RawNYUAD <- read_spss("data/raw data/Snowball Corona Long-Term Coverage - Baseline - Copy_April 8, 2020_03.41.sav")
dt0RawNYUAD$source <- "NYU-AD"

# merge adn fill missing
dt0Raw <- plyr::rbind.fill(dt0RawRUG, dt0RawNYUAD)

rm(dt0RawRUG, dt0RawNYUAD)
```

The raw data set includes `r length(dt0Raw)` variables for `r nrow(dt0Raw)` cases.   


## **Data Quality**   

### Filter: Preview Responses
Filter the Preview responses.
```{r preview, echo=T, warning=F, message=F}
# flag Preview Responses
dt1Preview <- dt0Raw %>%
  mutate(FilterPreview = labelled(ifelse(Status == 0,0,1),
                                  labels = c(preview = 1), label="Filter: survey preview response"))
```


### Filter: Survey Progress (drop out)  
<!-- https://cran.r-project.org/web/packages/naniar/vignettes/naniar-visualisation.html -->

Inspecting missing data in the items.

```{r Missing, echo=T, warning=F, message=F}
# Table: Missing Data per item
dt1Preview %>%
  dplyr::select(-starts_with("t_"), -starts_with("Pol")) %>% #drop timers and Political orientation (because of translation missingness)
  dplyr::select_if(~sum(is.na(.)) > 0) %>% # remove all variables that have no missingess
  naniar::miss_var_summary(.) %>% # by variable summary of missingness proportion
  DT::datatable(.,
                colnames = c("Variable", "Number Missing", "Percentage Missing"),
                filter = 'top',
                extensions = 'Buttons',
                options = list(
                  columnDefs = list(list(className = 'dt-center')),
                  #autoWidth = TRUE,
                  dom = 'Bfrtlip',
                  buttons = c('copy', 'csv', 'excel', 'pdf', 'print'))) %>%
  DT::formatRound('pct_miss', digits = 2)
  
# Plot: Missing Data per item
dt1Preview %>%
  dplyr::select(-starts_with("t_"), -starts_with("Pol")) %>% #drop timers and Political orientation (because of translation missingness)
  dplyr::select_if(~sum(is.na(.)) > 0) %>% # remove all variables that have no missingess
  naniar::gg_miss_var(.) # visualize by variable summary of missingness proportion

# Plot: Missing Data cumulative
dt1Preview %>%
  dplyr::select(-starts_with("t_"), -starts_with("Pol")) %>% #drop timers and Political orientation (because of translation missingness)
  dplyr::select_if(~sum(is.na(.)) > 0) %>% # remove all variables that have no missingess
  naniar::gg_miss_var_cumsum(.) # missingness development over survey

# Co-occurences of missingess - too many variables
#dt0Raw %>%
#  dplyr::select(-starts_with("t_"), -starts_with("Pol")) %>% #drop timers and Political orientation (because of translation missingness)
#  dplyr::select_if(~sum(is.na(.)) > 0) %>% # remove all variables that have no missingess
#  naniar::gg_miss_upset(., nsets = n_var_miss(.)) # visualize missingess co-occurences

# set time cut-off criterion:
progressCutOff <- 97 #cut-off criterion in percent
progressFilter <- dt1Preview %>%
  dplyr::select(Progress) %>%
  mutate(out = Progress < progressCutOff)

progressCutOffPerc <- round(sum(progressFilter$out)/nrow(progressFilter)*100,2) # percent of missing data with current cut-off criterion

# plot histogram and missing
ggplot(data=progressFilter, aes(x=Progress, fill=out)) +
  geom_histogram(bins=50,
                 alpha=.6) +
  geom_vline(xintercept = progressCutOff, 
             color = "darkred",
             linetype = "longdash") +
  geom_text(aes(x=progressCutOff, label=paste0("Progress cut-off: ",progressCutOff,"%\n"), y=Inf), 
            hjust = 1,
            colour="darkred", 
            angle=90) +
  geom_text(aes(x=progressCutOff, label=paste0("\ndata loss: ",progressCutOffPerc,"%"), y=Inf), 
            hjust = 1,
            colour="darkred", 
            angle=90) +
  #scale_x_continuous(breaks = seq(0, 100,3)) +
  scale_fill_manual(values=c("darkgrey","darkred")) +
  labs(title = "Histogram: Survey Progress", 
       x = "Survey Progress [Percent completed]",
       y = "Frequency Count") +
  theme_Publication() +
  theme(legend.position = "none")

# flag anyone with less than 5 minutes survey duration
dt2Progress <- dt1Preview %>%
  mutate(FilterProgress = labelled(ifelse(Progress < progressCutOff,1,0),
                               labels = c(`consent` = 1), label="Filter: Did not see debriefing"))

rm(progressFilter, progressCutOff, progressCutOffPerc)
```


### Filter: Short Duration on Survey   
Filter survey responses that were shorter than 5 minutes.   
```{r Duration, echo=T, warning=F, message=F}
# truncate data:
tOutlierHigh <- dt2Progress %>%
  dplyr::select(Duration__in_seconds_) %>%
  filter(Duration__in_seconds_<=stats::median(Duration__in_seconds_)+stats::mad(Duration__in_seconds_)*3.5) %>%
  mutate(Minutes = Duration__in_seconds_/60)

# set time cut-off criterion:
tCutOff <- 5 #cut-off criterion in minutes
# CJ: This might be a bit strict, I suspect that I completed it in <10 minutes. 
tCutOffPerc <- round(sum(tOutlierHigh$Minutes<tCutOff)/nrow(dt2Progress)*100,2) # percent of missing data with current cut-off criterion
tOutlierHigh$out <- tOutlierHigh$Minutes < tCutOff

# plot histogram and missing
ggplot(data=tOutlierHigh, aes(x=Minutes, fill=out)) +
  geom_histogram(bins=round(max(tOutlierHigh$Minutes),0),
                 alpha=.6) +
  geom_vline(xintercept = tCutOff, 
             color = "darkred",
             linetype = "longdash") +
  geom_text(aes(x=tCutOff, label=paste0("time cut-off: ",tCutOff," Minutes\n"), y=Inf), 
            hjust = 1,
            colour="darkred", 
            angle=90) +
  geom_text(aes(x=tCutOff, label=paste0("\ndata loss: ",tCutOffPerc,"%"), y=Inf), 
            hjust = 1,
            colour="darkred", 
            angle=90) +
  scale_x_continuous(breaks = seq(0, round(max(tOutlierHigh$Minutes),0), 5)) +
  scale_fill_manual(values=c("darkgrey","darkred")) +
  labs(title = "Truncated Histogram: Survey Duration", 
       x = "Duration [Mintues]",
       y = "Frequency Count",
       caption = "Notes:
       (1) Truncated: all participants who took less time than Median+3.5*MAD
       (2) Each bin represents one Minute") +
  theme_Publication() +
  theme(legend.position = "none")

# flag anyone with less than 5 minutes survey duration
dt3Time <- dt2Progress %>%
  mutate(FilterTime = labelled(ifelse(Duration__in_seconds_ > tCutOff*60,0,1),
                               labels = c(`extremely quick` = 1), label="Filter: Took less than 5 minutes on survey"))


rm(tOutlierHigh, tCutOff, tCutOffPerc)
# flag anyone with less than 5 minutes survey duration
dt2Time <- dt1Preview %>%
  mutate(FilterTime = labelled(ifelse(Duration__in_seconds_ > 300,0,1),
                               labels = c(`extremely quick` = 1), label="Filter: Took less than 5 minutes on survey"))
```


### Filter: Straightliners   
Filter participants, who have straightlined on the job insecurity scale, which includes a reverse coded item. We only flag people who straightlined outside the median categories because all "neither agree nor disagree" might be meaningful response.   
```{r Straightliner, echo=T, warning=F, message=F}
# CheckMissingness pattern
naniar::gg_miss_upset(dt3Time %>%
  dplyr::select(ResponseId, jbInsec01, jbInsec02, jbInsec03) %>%
  na_if(., -99) # all -99 into <NA>
)

# isolate respondents who have straightlined outside a the median categories (b/c all "neither agree nor disagree" might be meaningful response) 
jobinsecRed <- dt3Time %>%
  dplyr::select(ResponseId, jbInsec01, jbInsec02, jbInsec03) %>%
  na_if(., -99) %>% # all -99 into <NA>
  na.omit() %>% # remove people who have missing data on one of the three items
  mutate(mean = rowMeans(dplyr::select(., c("jbInsec01", "jbInsec02", "jbInsec03"))), 
         sd = matrixStats::rowSds(as.matrix(dplyr::select(., c("jbInsec01", "jbInsec02", "jbInsec03"))))) %>% # calculate row-means and row-sds 
  filter(sd == 0, mean != 0)

# flag anyone who straightlined on job insecurity
dt4Straightliner <- dt3Time %>%
  mutate(FilterStraightliner = labelled(ifelse(!ResponseId %in% jobinsecRed$ResponseId,0,1),
                                        labels = c(straightliner = 1), label="Filter: straightliner on Job Insecurity"))
rm(jobinsecRed)
```


## **Data Preparation**   
Note: For each of the scales we do an item analysis, and combine the items to the mean- (.m), and factor scores (.fa). We also centered (.c) and standardized (.z) the mean scores. Most of these items are not labelled for SPSS yet. For centering and standardizing to be accurate, we first filter the relevant criteria.

### Recoded Items   
Re-coding reverse coded items and the Qualtrics language codes.
```{r recode, echo=T, warning=F, message=F}
# Recoded Items
dt5newVars <- dt4Straightliner %>%
  mutate(jbInsec02_R = labelled(recode(as.numeric(jbInsec02), `-2` = 2, `-1` = 1, `0` = 0, `1` = -1, `2` = -2, `-99` = -99),
                                labels = NULL, label="Job Insecurity 02 (re-coded)"),
         bor03_R = labelled(recode(as.numeric(bor03), `-2` = 2, `-1` = 1, `0` = 0, `1` = -1, `2` = -2),
                            labels = NULL, label="Boredom 03 (re-coded)"))
# Language
# Import Qualtrics Language Codes
qualtricsLanguage <- read_excel("data/raw data/qualtricsLanguageCodes.xlsx")
dt5newVars <- merge(x=dt5newVars, y=qualtricsLanguage, by="Q_Language", all.x=TRUE)
rm(qualtricsLanguage)
```

### Filter Participants
```{r filtBefCalc, echo=T, warning=F, message=F}
dt5newVars <- dt5newVars %>%
  filter(FilterPreview == 0,
         FilterProgress == 0,
         FilterTime == 0,
         FilterStraightliner == 0)

# TO DO: REMOVE TESTS (OFTEN STRING)
```

### Country
We currently have `r length(table(dt5newVars$country))` different free text country responses. Here we aim to consolidate them into one variable.
```{r Country, echo=T, warning=F, message=F}
# CJ: Just as a benchmark, geolocate IP address. Can always use this if a free 
# CJ: text country response does not resolve 
# MA: should only be used for those that agree; also VPNs are problematic
# library(rgeolocate)
# file <- system.file("extdata","GeoLite2-Country.mmdb", package = "rgeolocate")
# geolocations <- maxmind(dt5newVars$IPAddress, file, c("continent_name", "country_code", "country_name"))
# dt5newVars$coded_country_ip <- geolocations$country_name
# rm(geolocations)

# CJ: This is a slightly cleaner, faster, and more informative regex based approach.
# CJ: The function and dictionary (based on the code below, some errors corrected) 
# CJ: is in

dt5newVars$country <- dt5newVars$country %>%
  tolower() %>% #make them lower case
  gsub(" ", "", ., fixed = TRUE) %>% # remove white space
  as.character() #make sure everything is characters

source("./scripts/functions/dictionary_functions.R")

# sourcing seems to destroy everything
country_dict <- list('Albania' = c('albania'),
                     'Algeria' = c('algeri','الجزائر','algérie','الجزاءر'),
                     'Andorra' = c('andorra'),
                     'Argentina' = c('argentina',  'arge'),
                     'Australia' = c('australia',  'austrija'),
                     'Austria' = c('austria',  'sterreich'),
                     'Azerbaijan' = c('azerba'),
                     'Bahrain' = c('bahrain'),
                     'Bangladesh' = c('bangladesh'),
                     'Belgium' = c('belg',  'bélgica', 'бельгия'),
                     'Bosnia and Herzegovina' = c('bosnaihercegovina'),
                     'Botswana' = c('botswana'),
                     'Brazil' = c('brazil',  'brasil'),
                     'Bulgaria' = c('bulgaria', 'българия'),
                     'Cameroon' = c('camer'),
                     'Canada' = c('canad',  'vancouver', 'канада'),
                     'Chile' = c('^chile$'),
                     'China' = c('^china', '中国', '中华人民共和国'),
                     'Colombia' = c('colombia'),
                     'Costa Rica' = c('costa'), 
                     'Croatia' = c('croa', "hrvatsk"),
                     'Cyprus' = c('cyp', '^κ...ο.', '^κ...ο'), 
                     'Czech Republic' = c('czech',  'checa'),
                     'Denmark' = c('mark'),
                     'Dominican Republic' = c('domin'),
                     'Ecuador' = c('ecuador'),
                     'Egypt' = c('مصر'),
                     'El Salvador' = c('salvador'),
                     'Estonia' = c('estonia'),
                     'Finland' = c('finland'),
                     'France' = c('france',  'francia',  'frankrijk'),
                     'Germany' = c('germany',  'deutschland',  'alemania',  'germania',  '^almanya$', 'allemagne',  'berlin',  'duitsland', 'γ.ρ.....'),
                     'Greece' = c('greece',  'grecia', 	'.λλ...', '.λλ..'),
                     'Guatemala' = c('guat'),
                     'Hong Kong S.A.R.' = c('hong.{0,}kong', '香港'),
                     'Hungary' = c('hungary', '^magyarorsz', 'magyar', 'ungarn'),
                     'Iceland' = c('iceland'),
                     'India' = c('india'),
                     'Indonesia' = c('^indonesia$',  'indonesian',  'kota, tarakan',  'imdonesia',  'indònesia',  'jakarta'),
                     'Iran' = c('iran'),
                     'Iraq' = c('iraq',  'العراق'),
                     'Ireland' = c('^ireland$',  'irlanda', 'ιρλ.....'),
                     'Israel' = c('القدس', 'israel', 'اللد',  'اسرائيل',  'كفر, قاسم',  'isreal',  'רמלה', 'الرمله'), 
                     'Italy' = c('ital',  'sardegna',  'bisceglie',  'ladispoli',  'castelforte',  'milano',  '^roma$', 'dorgali',  'bari',  'bologna',  'brescia',  'cala, gonone',  'chieti',  'ferentino',  'frosinone',  'gragnano, lucca, ',  'guidonia',  'itaia',  'italya',  'mareno, di, piave',  'modena',  'pellizzano',  'predazzo',  'refrontolo',  'cosma, e, damiano',  'scalea',  'scauri',  'segni',  'settimo, vittone',  'susegana',  'terralba',  'trento',  'treviso',  'tezze, di, piave',  'valmontone',  'vergato',  'veneto',  'gragnano, lucca'),
                     'Jamaica' = c('jamaica'),
                     'Japan' = c('japan',  'giappone',  'japonya', '日本'),
                     'Jordan' = c('jordan', 'الأردن'),
                     'Kazakhstan' = c('казахстан', 'kazakhstan'),
                     'Kenya' = c('kenia'),
                     'Laos' = c('laos'),
                     'Latvia' = c('latvia'),
                     'Lebanon' = c('lebanon',  'liban'),
                     'Libya' = c('ليبيا'),
                     'Luxembourg' = c('lux'),
                     'Malaysia' = c('malay'),
                     'Malta' = c('malta'),
                     'Mauritius' = c('maurice'),
                     'Mexico' = c('mexico',  'méxico'),
                     'Montenegro' = c('crnagora'),
                     'Morocco' = c('المغرب',  'maroc'),
                     'Myanmar' = c('myanmar'),
                     'Nepal' = c('nepal'),
                     'Netherlands' = c('netherland',  'nederland',  'niederlande',  'belanda',  '^nl$',  'olanda',  'paesi, bassi',  'paesi bassi',  'bajos',  'gelderland',  'hollanda', 'paes.+bass.'),
                     'New Zealand' = c('new.+zeal', 'newzealand',  'neuseeland'),
                     'Nigeria' = c('nigeria'),
                     'Norway' = c('norway'),
                     'Oman' = c('^oman$'),
                     'Pakistan' = c('pakistan',  'abbottabad',  'peshawar'),
                     'Palestine' = c('palestine',  'فلسطين, ',  '^فلسطين$',  'الرملة'),
                     'Panama' = c('panam'), 
                     'Peru' = c('peru', 'perú'),
                     'Philippines' = c('phil',  'filipinas'),
                     'Poland' = c('poland',  'polonia', 'польша'),
                     'Portugal' = c('portugal'), 
                     'Qatar' = c('qatar'),
                     'Republic of Serbia' = c('srbija',  'serbia',  'србија'),
                     'Romania' = c('romania', 'rom.nia'),
                     'Russia' = c('россия'),
                     'Saudi Arabia' = c('riyad',  'saud.+arab',  'arabia, saudita',  '^saudi$',  'kingdom, of, saudia, arabia',  'ksa',  'k\\.s\\.a',  'arabie, saoudite',  'الرياض',  'السعودية',  'السعوديه', 'emira+arab'),
                     'Republic of Serbia' = c('srbiji', 's.erbia'),
                     'Singapore' = c('singapore'),
                     'Slovakia' = c('slova'),
                     'South Africa' = c('africa',  '^sa$',  'sudáfrica',  'western, cape', 'southaf...'),
                     'South Korea' = c('korea',  'güney, kore'),
                     'Spain' = c('spain',  'esp',  'spagna',  'spanien',  'catal',  'euskal, herria',  'basque',  'eapaña',  'esapaña',  'madrid',  'montalbán, de, córdoba',  'pais, vasco',  'spanje'),
                     'Sweden' = c('weden'),
                     'Switzerland' = c('schweiz',  'suiza',  'svizzera',  'zwitserland',  'switzerland', 'suisse'),
                     'Taiwan' = c('taiwan', '台灣'),
                     'Thailand' = c('^thailand$'),
                     "Trinidad and Tobago" = c("trinid"),
                     'Tunisia' = c('tuni',  'تونس'),
                     'Turkey' = c('turkey',  't.rk.y.', 't.rk.{0,2}', "t[a-z]rkiye"), #"'\u00fcrkiye'"
                     'Ukraine' = c('ukraine', 'у.ра..а'),
                     'United Arab Emirates' = c('الخرج',  'united, arab, emirates', 'الامارات', '^uae$', 'arabemirates', 'لعربيةالمتحدة'),
                     'United Kingdom' = c('uni.+kin',  '^uk$',  'reino, unido',  'britain',  'regno, unito',  'u\\.k\\.',  'بريطانيا',  'the, uk',  'u, k',  'verenigd, koninkrijk',  'windsor',  'scotland',  'england',  'wales',  'ingiltere',  'northern, ireland',  'egland',  '^gb$',  'n, ireland',  'schotland',  'scozia', '英国', 'ngiltere', 'n.{4,9}ireland', 'reinounido'),
                     'United Republic of Tanzania' = c('tanzania'),
                     'United States of America' = c('america', '^usa', 'u.s.a',  'uni.+stat', 'uni.+merica',  '^america$',  '^u.{0,1}s.{0,1}$',  'esta.+unid',  'colorado',  '^us$',  'xas',  'sates',  'amerika, serikat',  'california',  'corlifornia',  'états-unis', 'puerto, rico',  '^tx$',  '^tn$',  'u, s', '美国', 'new+york', 'сша', 'un..edsta.es', 'arizona'), 
                     'Uruguay' = c('urug'),
                     'Uzbekistan' = c('u.{2,5}istan'),
                     'Venezuela' = c('^venezuela$'),
                     'Vietnam' = c('vietnam')
                     )


country_matches <- cat_words(dt5newVars$country, country_dict) 
country_matches$words[country_matches$words %in% names(country_matches$unmatched)] <- NA
# Check unmatched strings, fix common ones
## View(country_matches$unmatched)
# Check duplicates, and which regular expressions triggered them
## View(country_matches$dup)
dt5newVars$coded_country <- country_matches$words
dt5newVars$coded_country[dt5newVars$coded_country %in% names(country_matches$unmatched)] <- NA


# CODE FOR EXPORT:
# country_entry <- dt5newVars$country
# country_names <- rnaturalearth::ne_countries(scale = "medium")$admin
# namTR <- paste0("data/cleaned data/countries ", format(Sys.time(), format = "%F %H-%M %Z"),".RData")
# save(country_entry, country_names, file = namTR)
```
<br>
<div class="alert alert-warning">
<strong><i class="fa fa-exclamation-triangle"></i> Action needed:</strong> <br> 
We currently have `r length(unique(dt5newVars$country))` different free text country responses. The most recent codes leaves `r sum(country_counts$n[country_counts$country != ""])` responses are still not consolidated.
</div>

### Visualize Response Rates (maybe moved somewhere else?)
We visualize how many responses we have per day.
```{r RespVis, echo=T, warning=F, message=F}
tmp <- setNames(data.frame(table(lubridate::round_date(dt5newVars$EndDate, unit = "12 hours"))),c("Date","Count"))
ggplot(tmp, aes(x=Date, y = Count))+
   geom_line(group = 1)+
   theme_bw()+
   # scale_y_continuous(limits = c(0, 158),
   #                    breaks = seq(0,160,20))+
   theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 8))

```


### Political Orientation   
Political orientation was measured per language. We merge these variables here.    
```{r PolOr, echo=T, warning=F, message=F}
# clean-up country coding:
rm(country_counts)

# political orientation
dt5newVars <- dt5newVars %>%
  mutate(PolOrX = labelled(rowSums(dplyr::select(., ends_with("_x")), na.rm = T), 
                           labels = NULL, label="Political Compass X-Coordinate"),
         PolOrY = labelled(rowSums(dplyr::select(., ends_with("_y")), na.rm = T), 
                           labels = NULL, label="Political Compass Y-Coordinate"),
         PolOrAuthoritarianLeft = rowSums(dplyr::select(., ends_with("_Authoritarian_Left")), na.rm = T),
         PolOrAuthoritarianLeftLab = dplyr::recode(PolOrAuthoritarianLeft, `1` =  "Authoritarian Left", `0` = ""),
         PolOrAuthoritarianRight = rowSums(dplyr::select(., ends_with("_Authoritarian_right")), na.rm = T),
         PolOrAuthoritarianRightLab = dplyr::recode(PolOrAuthoritarianRight, `1` =  "Authoritarian Right", `0` = ""),
         PolOrLibertarianLeft = rowSums(dplyr::select(., ends_with("_Libertarian_Left")), na.rm = T),
         PolOrLibertarianLeftLab = dplyr::recode(PolOrLibertarianLeft, `1` =  "Libertarian Left", `0` = ""),
         PolOrLibertarianRight = rowSums(dplyr::select(., ends_with("_Libertarian_Right")), na.rm = T),
         PolOrLibertarianRightLab = dplyr::recode(PolOrLibertarianRight, `1` =  "Libertarian Right", `0` = ""),
         PolOrOther = rowSums(dplyr::select(., ends_with("_Other")), na.rm = T),
         PolOrOtherLab = dplyr::recode(PolOrOther, `1` =  "Other", `0` = ""),
         PolOrCat = paste0(PolOrAuthoritarianLeftLab, 
                           PolOrAuthoritarianRightLab,
                           PolOrLibertarianLeftLab,
                           PolOrLibertarianRightLab,
                           PolOrOtherLab), 
         PolOrCat = as.factor(na_if(PolOrCat, ""))) %>%
  dplyr::select(-starts_with("Pol"),
         PolOrX,
         PolOrY,
         PolOrCat)
attr(dt5newVars$PolOrCat,'label') <- 'Political Orientation Quadrant'
```

### Affect    
<!-- TO DO: Write function for item analysis and scale construction -->


#### High Arousal Negative   
```{r affHighNeg, echo=T, results='asis', warning=F, message=F}
# High Arousal Negative
## Anger not measured in wave 1
pairs.panels.new(dt5newVars %>% dplyr::select(affAnx, affNerv))

cat("<br>")

dt5newVars$affHighNeg.m <- scoreItems(keys=c(1,1), items = dt5newVars %>% dplyr::select(affAnx, affNerv), min = 1, max = 5)$scores

as.data.frame(psych::describe(dt5newVars$affHighNeg.m, skew=F)) %>%
  mutate(vars = "High Arousal Negative Affect") %>%
  kable(., caption = "High Arousal Negative Affect: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$affHighNeg.c <- scale(dt5newVars$affHighNeg.m, scale = F, center = T)
dt5newVars$affHighNeg.z <- scale(dt5newVars$affHighNeg.m, scale = T)
dt5newVars$affHighNeg.fa <- fa(dt5newVars %>% dplyr::select(affAnx, affNerv))$scores
```

#### Low Arousal Negative Affect  
```{r affLowNeg, echo=T, results='asis', warning=F, message=F}
# Low Arousal Negative Affect
ia.affLowNeg <- dt5newVars %>%
    dplyr::select(affBor, affExh, affDepr) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.affLowNeg$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.affLowNeg)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(affBor, affExh, affDepr))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Low Arousal Negative Affect: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(affBor, affExh, affDepr))

cat("<br>")

dt5newVars$affLowNeg.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(affBor, affExh, affDepr), min = 1, max = 5)$scores

as.data.frame(psych::describe(dt5newVars$affLowNeg.m, skew=F)) %>%
  mutate(vars = "Low Arousal Negative Affect") %>%
  kable(., caption = "Low Arousal Negative Affect: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$affLowNeg.c <- scale(dt5newVars$affLowNeg.m, scale = F, center = T)
dt5newVars$affLowNeg.z <- scale(dt5newVars$affLowNeg.m, scale = T)
dt5newVars$affLowNeg.fa <- fa(dt5newVars %>% dplyr::select(affBor, affExh, affDepr))$scores
```

#### Low Arousal Positive Affect  
```{r affLowPos, echo=T, results='asis', warning=F, message=F}
# Low Arousal Positive Affect
ia.affLowPos <- dt5newVars %>%
    dplyr::select(affCalm, affContent, affRel) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.affLowPos$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.affLowPos)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(affCalm, affContent, affRel))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Low Arousal Positive Affect: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(affCalm, affContent, affRel))

cat("<br>")

dt5newVars$affLowPos.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(affCalm, affContent, affRel), min = 1, max = 5)$scores

as.data.frame(psych::describe(dt5newVars$affLowPos.m, skew=F)) %>%
  mutate(vars = "Low Arousal Positive Affect") %>%
  kable(., caption = "Low Arousal Positive Affect: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$affLowPos.c <- scale(dt5newVars$affLowPos.m, scale = F, center = T)
dt5newVars$affLowPos.z <- scale(dt5newVars$affLowPos.m, scale = T)
dt5newVars$affLowPos.fa <- fa(dt5newVars %>% dplyr::select(affCalm, affContent, affRel))$scores
```

#### High Arousal Positive Affect  
```{r affHighPos, echo=T, results='asis', warning=F, message=F}
# High Arousal Positive Affect
ia.affHighPos <- dt5newVars %>%
    dplyr::select(affEnerg, affExc, affInsp) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.affHighPos$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.affHighPos)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(affEnerg, affExc, affInsp))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "High Arousal Positive Affect: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(affEnerg, affExc, affInsp))

cat("<br>")

dt5newVars$affHighPos.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(affEnerg, affExc, affInsp), min = 1, max = 5)$scores

as.data.frame(psych::describe(dt5newVars$affHighPos.m, skew=F)) %>%
  mutate(vars = "High Arousal Positive Affect") %>%
  kable(., caption = "High Arousal Positive Affect: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$affHighPos.c <- scale(dt5newVars$affHighPos.m, scale = F, center = T)
dt5newVars$affHighPos.z <- scale(dt5newVars$affHighPos.m, scale = T)
dt5newVars$affHighPos.fa <- fa(dt5newVars %>% dplyr::select(affEnerg, affExc, affInsp))$scores
```

### Loneliness
```{r lone, echo=T, results='asis', warning=F, message=F}
ia.lone<- dt5newVars %>%
    dplyr::select(starts_with("lone")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.lone$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.lone)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("lone")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Loneliness: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("lone")))

cat("<br>")

dt5newVars$lone.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(starts_with("lone")), min = 1, max = 5)$scores

as.data.frame(psych::describe(dt5newVars$lone.m, skew=F)) %>%
  mutate(vars = "Loneliness") %>%
  kable(., caption = "Loneliness: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$lone.c <- scale(dt5newVars$lone.m, scale = F, center = T)
dt5newVars$lone.z <- scale(dt5newVars$lone.m, scale = T)
dt5newVars$lone.fa <- fa(dt5newVars %>% dplyr::select(starts_with("lone")))$scores
```  

### Boredom
```{r bore, echo=T, results='asis', warning=F, message=F}
ia.bor<- dt5newVars %>%
    dplyr::select(starts_with("bor0"), -bor03) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.bor$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.bor)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("bor0"), -bor03))
```
<div class="alert alert-info">
<strong><i class="fa fa-exclamation-triangle"></i> Item dropped:</strong> <br> 
Item three was not well behaved. It seems to measure something else. We dropped it for now.
</div>

```{r bore.red, echo=T, results='asis', warning=F, message=F}

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("bor0"), -bor03, -bor03_R))

cat("<br>")

dt5newVars$bor.m <- scoreItems(keys=c(1,1), items = dt5newVars %>% dplyr::select(starts_with("bor0"), -bor03, -bor03_R), min = -3, max = 3)$scores

as.data.frame(psych::describe(dt5newVars$bor.m, skew=F)) %>%
  mutate(vars = "Boredom") %>%
  kable(., caption = "Boredom: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$bor.c <- scale(dt5newVars$bor.m, scale = F, center = T)
dt5newVars$bor.z <- scale(dt5newVars$bor.m, scale = T)
dt5newVars$bor.fa <- fa(dt5newVars %>% dplyr::select(starts_with("bor0"), -bor03, -bor03_R))$scores
```
  
### Isolation
```{r iso, echo=T, results='asis', warning=F, message=F}
cat(crayon::bold("Offline Isolation"))
ia.isoPers <- dt5newVars %>%
    dplyr::select(ends_with("inPerson")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.isoPers$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.isoPers)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(ends_with("inPerson")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Isolation offline: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(ends_with("inPerson")))

cat("<br>")

dt5newVars$isoPers.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(ends_with("inPerson")), min = 0, max = 7)$scores

as.data.frame(psych::describe(dt5newVars$isoPers.m, skew=F)) %>%
  mutate(vars = "Isolation offline") %>%
  kable(., caption = "Isolation offline: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$isoPers.c <- scale(dt5newVars$isoPers.m, scale = F, center = T)
dt5newVars$isoPers.z <- scale(dt5newVars$isoPers.m, scale = T)
dt5newVars$isoPers.fa <- fa(dt5newVars %>% dplyr::select(ends_with("inPerson")))$scores

cat(crayon::bold("Online Isolation"))
ia.isoOnl <- dt5newVars %>%
    dplyr::select(ends_with("online")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.isoOnl$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.isoOnl)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(ends_with("inPerson")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Isolation online: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(ends_with("online")))

cat("<br>")

dt5newVars$isoOnl.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(ends_with("online")), min = 0, max = 7)$scores

as.data.frame(psych::describe(dt5newVars$isoPers.m, skew=F)) %>%
  mutate(vars = "Isolation online") %>%
  kable(., caption = "Isolation online: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$isoOnl.c <- scale(dt5newVars$isoOnl.m, scale = F, center = T)
dt5newVars$isoOnl.z <- scale(dt5newVars$isoOnl.m, scale = T)
dt5newVars$isoOnl.fa <- fa(dt5newVars %>% dplyr::select(ends_with("online")))$scores

# Leave House
as.data.frame(psych::describe(dt5newVars$houseLeave, skew=F)) %>%
  mutate(vars = "Leaving House") %>%
  kable(., caption = "Leaving House: Item Descriptive", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")
```

### Government Response
No responses yet
```{r gov, echo=T, results='asis', warning=F, message=F}
as.data.frame(psych::describe(dt5newVars$extC19Msg)) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Government Response: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

ggplot(dt5newVars, aes(x = extC19Msg)) +
  geom_histogram(binwidth=1, alpha=0.5) +
  #geom_density(alpha=0.6)+
  labs(title="Government Response distribution",x="Government Response", y = "Frequency") +
  theme_Publication()
```

### Community Response
```{r community, echo=T, results='asis', warning=F, message=F}
ia.ext <- dt5newVars %>%
    dplyr::select(starts_with("extC19"), -extC19Msg) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.ext$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.ext)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("extC19"), -extC19Msg))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Community response: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("extC19"), -extC19Msg))

cat("<br>")

dt5newVars$ext.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(starts_with("extC19"), -extC19Msg), 
                             min = 1, max = 6)$scores

as.data.frame(psych::describe(dt5newVars$ext.m, skew=F)) %>%
  mutate(vars = "Community response") %>%
  kable(., caption = "Community response: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$ext.c <- scale(dt5newVars$ext.m, scale = F, center = T)
dt5newVars$ext.z <- scale(dt5newVars$ext.m, scale = T)
dt5newVars$ext.fa <- fa(dt5newVars %>% dplyr::select(starts_with("extC19"), -extC19Msg))$scores
```

### Behavioral Response
```{r beh, echo=T, results='asis', warning=F, message=F}
ia.beh <- dt5newVars %>%
    dplyr::select(starts_with("c19per")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.beh$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.beh)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("c19per")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Behavioral response: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("c19per")))

cat("<br>")

dt5newVars$beh.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(starts_with("c19per")), 
                             min = -3, max = 3)$scores

as.data.frame(psych::describe(dt5newVars$beh.m, skew=F)) %>%
  mutate(vars = "Behavioral response") %>%
  kable(., caption = "Behavioral response: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$beh.c <- scale(dt5newVars$beh.m, scale = F, center = T)
dt5newVars$beh.z <- scale(dt5newVars$beh.m, scale = T)
dt5newVars$beh.fa <- fa(dt5newVars %>% dplyr::select(starts_with("c19per")))$scores
```

### Hope and Efficacy
```{r hopeEff, echo=T, results='asis', warning=F, message=F}
as.data.frame(psych::describe(dt5newVars$c19Hope)) %>%
  mutate(vars = "Hope") %>%
  kable(., caption = "Hope: Item Descriptive", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

ggplot(dt5newVars, aes(x = c19Hope)) +
  geom_histogram(binwidth=1, alpha=0.5) +
  #geom_density(alpha=0.6)+
  labs(title="Hope distribution",x="Corona Virus Hope", y = "Frequency") +
  theme_Publication()
  
as.data.frame(psych::describe(dt5newVars$c19Eff)) %>%
  mutate(vars = "Efficacy") %>%
  kable(., caption = "Efficacy: Item Descriptive", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

ggplot(dt5newVars, aes(x = c19Eff)) +
  geom_histogram(binwidth=1, alpha=0.5) +
  #geom_density(alpha=0.6)+
  labs(title="Efficacy distribution",x="Corona Virus Efficacy", y = "Frequency") +
  theme_Publication()
```

### State Paranoia
```{r para, echo=T, results='asis', warning=F, message=F}
ia.para <- dt5newVars %>%
    dplyr::select(starts_with("para")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.para$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.para)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("para")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "State Paranoia: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("para")))

cat("<br>")

dt5newVars$para.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(starts_with("para")), 
                             min = 0, max = 10)$scores

as.data.frame(psych::describe(dt5newVars$para.m, skew=F)) %>%
  mutate(vars = "State Paranoia") %>%
  kable(., caption = "State Paranoia: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$para.c <- scale(dt5newVars$para.m, scale = F, center = T)
dt5newVars$para.z <- scale(dt5newVars$para.m, scale = T)
dt5newVars$para.fa <- fa(dt5newVars %>% dplyr::select(starts_with("para")))$scores
```

### Conspiracy Theory
```{r consp, echo=T, results='asis', warning=F, message=F}
ia.consp <- dt5newVars %>%
    dplyr::select(starts_with("consp")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.consp$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.consp)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("consp")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Conspiracy Theory: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("consp")))

cat("<br>")

dt5newVars$consp.m <- scoreItems(keys=c(1,1,1), items = dt5newVars %>% dplyr::select(starts_with("consp")), 
                             min = 0, max = 10)$scores

as.data.frame(psych::describe(dt5newVars$consp.m, skew=F)) %>%
  mutate(vars = "Conspiracy Theory") %>%
  kable(., caption = "Conspiracy Theory: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$para.c <- scale(dt5newVars$consp.m, scale = F, center = T)
dt5newVars$para.z <- scale(dt5newVars$consp.m, scale = T)
dt5newVars$para.fa <- fa(dt5newVars %>% dplyr::select(starts_with("consp")))$scores
```

### Job Insecurity
```{r jbinsc, echo=T, results='asis', warning=F, message=F}
ia.jobinsec<- dt5newVars %>%
    dplyr::select(starts_with("jbInsec"), -jbInsec02, -jbInsec04) %>%
    na_if(., -99) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.jobinsec$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.jobinsec)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("jbInsec"), -jbInsec02, -jbInsec04) %>% na_if(., -99))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Job insecurity: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("jbInsec"), -jbInsec02, -jbInsec04) %>% na_if(., -99))

cat("<br>")

dt5newVars$jobinsec.m <- scoreItems(keys=c(1,1,1), 
                                  items = dt5newVars %>% dplyr::select(starts_with("jbInsec"), -jbInsec02, -jbInsec04) %>% na_if(., -99),
                                  min = -2, max = 2)$scores

as.data.frame(psych::describe(dt5newVars$jobinsec.m, skew=F)) %>%
  mutate(vars = "Job insecurity") %>%
  kable(., caption = "Job insecurity: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$jobinsec.c <- scale(dt5newVars$jobinsec.m, scale = F, center = T)
dt5newVars$jobinsec.z <- scale(dt5newVars$jobinsec.m, scale = T)
dt5newVars$jobinsec.fa <- fa(dt5newVars %>% dplyr::select(starts_with("jbInsec"), -jbInsec02, -jbInsec04))$scores
```

### Financial Strain
```{r finance, echo=T, results='asis', warning=F, message=F}
ia.pfs<- dt5newVars %>%
    dplyr::select(starts_with("PFS0")) %>%
    Scale::Scale() %>%
    Scale::ItemAnalysis()
ia.pfs$rely   
cat("<br><br>A gls factor analysis was conducted. Items were regressed to a single factor. Their loadings are the following:")
as.data.frame(Scale::ReportTable(ia.pfs)) %>%
  kable(., row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

as.data.frame(psych::describe(dt5newVars %>% dplyr::select(starts_with("PFS0")))) %>%
  mutate(vars = rownames(.)) %>%
  kable(., caption = "Financial Strain: Item Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

cat("<br>")

pairs.panels.new(dt5newVars %>% dplyr::select(starts_with("PFS0")))

cat("<br>")

dt5newVars$pfs.m <- scoreItems(keys=c(1,1,1), 
                                  items = dt5newVars %>% dplyr::select(starts_with("PFS0")),
                                  min = -2, max = 2)$scores

as.data.frame(psych::describe(dt5newVars$pfs.m, skew=F)) %>%
  mutate(vars = "inancial Strain") %>%
  kable(., caption = "inancial Strain: Scale Descriptives", row.names = FALSE) %>% 
  kable_styling("hover", full_width = F, latex_options = "hold_position")

dt5newVars$pfs.c <- scale(dt5newVars$pfs.m, scale = F, center = T)
dt5newVars$pfs.z <- scale(dt5newVars$pfs.m, scale = T)
dt5newVars$pfs.fa <- fa(dt5newVars %>% dplyr::select(starts_with("PFS0")))$scores
```


## **Reduce to Relevant Variales**   
```{r keyVars, echo=T, warning=F, message=F}
# clean-up Item Analyses
rm(list=ls(pattern="ia"))

# remove directly identifiable data (with and without page timers)
dt6ReducedTimer <- dt5newVars %>%
  dplyr::select(-c(IPAddress, 
            RecipientLastName, 
            RecipientFirstName, 
            RecipientEmail, 
            ExternalReference, 
            LocationLatitude, 
            LocationLongitude,
            DistributionChannel,
            ICRec_0_TEXT,
            ICRec_1_TEXT))
dt6Reduced <- dt6ReducedTimer %>%
  dplyr::select(-starts_with("t_"))

# # remove filtered cases (with and without page timers)
# dt6ReducedTimerCases <- dt6ReducedTimer %>%
#   filter(FilterPreview == 0,
#          FilterProgress == 0,
#          FilterTime == 0,
#          FilterStraightliner == 0) %>%
#   dplyr::select(-starts_with("Filter"))
# dt6ReducedCases <- dt6Reduced %>%
#   filter(FilterPreview == 0,
#          FilterProgress == 0,
#          FilterTime == 0,
#          FilterStraightliner == 0) %>%
#   dplyr::select(-starts_with("Filter"))

as.Date(dt5newVars$EndDate) 

library("lubridate")
ContactList <- dt5newVars %>%
  filter(FilterPreview == 0,
         ICRec_1_TEXT!="",
         ymd_hms(dt5newVars$EndDate) < "2020-03-31 12:00:00 UTC") %>%
  dplyr::distinct(ICRec_1_TEXT, .keep_all = TRUE) %>%
  dplyr::select(ExternalDataReference = ResponseId, 
                Language = Q_Language, 
                Email = ICRec_1_TEXT,
                StartDateBaseline = StartDate, 
                EndDateBaseline = EndDate)

LanguageList <- as.data.frame(sort(table(dt6ReducedCases$language), decreasing = T))

# Dataframe for Shiny App
# load geo spatial data
library(rnaturalearth)
library(rnaturalearthdata)
world.data <- ne_countries(scale = "medium", returnclass = "sf")
unique(dt5newVars$coded_country)[!unique(dt5newVars$coded_country) %in% world.data$admin] # check whether all country names are spelled correctly

# all ISO-2 country code to dataframe and flags
shiny_prep <- merge(x = dt5newVars, y = world.data %>% dplyr::select(admin, iso_a2), by.x = "coded_country", by.y = "admin", all.x = T)
shiny_prep$flag <- sprintf("https://cdn.rawgit.com/lipis/flag-icon-css/master/flags/4x3/%s.svg", tolower(shiny_prep$iso_a2))

shiny_data <- shiny_prep %>%
  dplyr::select(coded_country,
         iso_a2,
         flag,
         # sample:
         language,
         gender,
         age,
         edu,
         PolOrCat,
         # affect individual:
         affAnx,
         affBor,
         affCalm,
         affContent,
         affDepr,
         affEnerg,
         affExc,
         affNerv,
         affExh,
         affInsp,
         affRel,
         # affect compound:
         affHighPos.m,
         affHighNeg.m,
         affLowPos.m,
         affLowNeg.m,
         # Government:
         extC19Msg,
         # Community:
         extC19Rules,
         extC19Punish,
         extC19Org,
         # Cognitive:
         c19Hope,
         c19Eff,
         lone.m,
         para.m,
         consp.m,
         # Behavior:
         c19perBeh01,
         c19perBeh02,
         isoPers.m,
         isoOnl.m
         )
```

## **Descriptives for Representativeness**
```{r rep, echo=T, warning=F, message=F}
ctry.rep2 <- dt5newVars %>%
  #filter(!is.na(coded_country)) %>%
  filter(!is.na(PLRAC19),
         !is.na(extC19Msg),
         !is.na(pfs.m),
         !is.na(consp.m),
         !is.na(lone.m)
         ) %>%
  filter_at(vars(jbInsec01,jbInsec02, jbInsec03, jbInsec04, PLRAEco),all_vars(!is.na(.))) %>%
  filter_at(vars(disc01,disc02, disc03),all_vars(!is.na(.))) %>%
  filter_at(vars(isoFriends_inPerson, isoOthPpl_inPerson, isoFriends_online, isoOthPpl_online),all_vars(!is.na(.))) %>%
  filter_at(vars(c19Hope, c19Eff, ecoHope, ecoEff),all_vars(!is.na(.))) %>%
  filter_at(vars(c19RCA01, c19RCA02, c19RCA03, ecoPerBeh01, ecoPerBeh02, ecoPerBeh03),all_vars(!is.na(.))) %>%
  filter_at(vars(c19NormShould, c19ProSo01, c19ProSo02, c19ProSo03),all_vars(!is.na(.))) %>%
  filter_at(vars(c19NormDo, extC19Rules, extC19Punish, extC19Org),all_vars(!is.na(.))) %>%
  filter_at(vars(c19ProSo01, c19ProSo02, c19ProSo03, c19ProSo04, ecoProSo01, ecoProSo02, ecoProSo03, ecoProSo04),all_vars(!is.na(.))) %>%
  group_by(coded_country) %>%
  dplyr::summarize(
    n = n(),
    gender_women = sum(gender == 1, na.rm = T),
    gender_men = sum(gender == 2, na.rm = T),
    gender_other = sum(gender == 3, na.rm = T),
    gender_na = sum(is.na(gender), na.rm = T),
    age_18to24 = sum(age == 1, na.rm = T),
    age_25to34 = sum(age == 2, na.rm = T),
    age_35to44 = sum(age == 3, na.rm = T),
    age_45to54 = sum(age == 4, na.rm = T),
    age_55to64 = sum(age == 5, na.rm = T),
    age_65to75 = sum(age == 6, na.rm = T),
    age_75to85 = sum(age == 7, na.rm = T),
    age_85plus = sum(age == 8, na.rm = T),
    age_na = sum(is.na(age), na.rm = T)
  )
```

## **Export**   
Export main dataframe as RData and SPSS sav files. We export versions with and without page timers
```{r export, echo=T, warning=F, message=F}
namSPSS <- paste0("data/cleaned data/Psycorona Baseline cleaned ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
namR <- paste0("data/cleaned data/Psycorona Baseline cleaned ", format(Sys.time(), format = "%F %H-%M %Z"),".RData")
namTSPSS <- paste0("data/cleaned data/Psycorona Baseline cleaned with page timer ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
namTR <- paste0("data/cleaned data/Psycorona Baseline cleaned with page timer ", format(Sys.time(), format = "%F %H-%M %Z"),".RData")
namCL <- paste0("data/cleaned data/Contact List ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
namLL <- paste0("data/cleaned data/Language List ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
namDemo <- paste0("data/cleaned data/Country Demographics ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")

write_sav(dt6Reduced, namSPSS)
write_sav(dt6ReducedTimer, namTSPSS)

save(dt6Reduced, file = namR)
save(dt6ReducedTimer, file = namTR)

# export for Shiny
saveRDS(shiny_data, file = "../PsyCorona-WebApp/data/reducedData.rds")

# export Contact List
#write.csv(ContactList, file = namCL)

# export Language List
#write.csv(LanguageList, file = namLL)

# export Country Demographics
write.csv(ctry.rep, file = namDemo)

rm(list=ls(pattern="nam"))
```
