---
title: "Psycorona - Data Sharinh"
subtitle: "Step by step description" 
author: "PsyCorona Gang"
date: "3/30/2020"
output:
  html_document: 
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
editor_options:
  chunk_output_type: console
---


<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>


```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  rm(list=ls()) # clear workspace
  gc # garbage collector
  
# Install and Load Packages
  #if(!require(pacman)) install.packages("pacman")
  # require(pacman)
  # pacman::p_load(psych, ggplot2, ggthemes, haven, data.table, dplyr, tidyr, Hmisc, mada, 
  #                knitr, kableExtra, naniar, stats, readxl, matrixStats, ISOcodes, pander,
  #                Scale)
lib <- c("psych", "ggplot2", "ggthemes", "haven", "data.table", "dplyr", "tidyr", "Hmisc", "mada", 
         "knitr", "kableExtra", "naniar", "stats", "readxl", "matrixStats", "ISOcodes", "pander", "Scale")

invisible(lapply(lib, library, character.only = TRUE))  
lapply(lib, library, character.only = TRUE)
rm(lib)  

# Load Custom Packages  
  source("./scripts/functions/fun.panel.R")
  source("./scripts/functions/themes.R")
  source("./scripts/functions/dictionary_functions.R")
  
# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(echo = TRUE)
```

Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.   

<br/>

## **Preparation**
In a first step we import the raw Qualtrics data, which was downloaded as an SPSS file.   
### Import Data
```{r LoadRawBase, echo=T, warning=F, message=F}
# Reset working directory to folder current file is saved in
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# Import Qualtrics Survey Data
  dtClean <- read_spss("data/cleaned data/Psycorona Baseline cleaned 2020-04-20 11-42 CEST.sav")
  dtAll <- read_spss("data/cleaned data/Psycorona Baseline cleaned - All2020-04-20 11-42 CEST.sav")
  
# Import Request sheet
  #dtReq <- read.csv("data/cleaned data/request/Variable Justification - Sheet1.csv", header = T)
  url <- gsheet::construct_download_url('docs.google.com/spreadsheets/d/13PFXsmgjrZBNddHodR2Z_80cjicN4s7yd8BbazKffx8/edit?usp=sharing', format = "csv", sheetid = NULL)
  dtReq <- gsheet::gsheet2tbl(url, sheetid = NULL); rm(url)
  dtReq <- dtReq[-c(1:2),]
```

### Function for Data
```{r fctExp, echo=T, warning=F, message=F}
stringOut <- NA #make var for fill out in function
nameOut <- function(df){
# if there is a B (baseline) paste the variable
  if (grepl("B",df[2], ignore.case = T)) {
    stringOut[1] = paste(df[1])
  } else {
    stringOut[1] = NA
  }
# if there is a W1 (baseline) paste w1 and the variable
  if (grepl("W1|Wave1|Wave 1",df[2], ignore.case = T)) {
    stringOut[2] = paste("w1_", df[1], sep = "")
  } else {
    stringOut[2] = NA
  }
  if (grepl("W2",df[2], ignore.case = T)) {
    stringOut[3] = paste("w2|Wave2|Wave 2_", df[1], sep = "")
  } else {
    stringOut[3] = NA
  }
  if (grepl("W3",df[2], ignore.case = T)) {
    stringOut[4] = paste("w3|Wave3|Wave 3_", df[1], sep = "")
  } else {
    stringOut[4] = NA
  }
  if (grepl("W4",df[2], ignore.case = T)) {
    stringOut[5] = paste("w4|Wave4|Wave 4_", df[1], sep = "")
  } else {
    stringOut[5] = NA
  }
  if (grepl("W5",df[2], ignore.case = T)) {
    stringOut[6] = paste("w5|Wave5|Wave 5_", df[1], sep = "")
  } else {
    stringOut[6] = NA
  }
return(stringOut)
}
# ADD WARNING IF ZIP CODE REQUESTED
```


The raw data set includes `r length(dt0Raw)` variables for `r nrow(dt0Raw)` cases.

### RMD 2 (Ben Guetzkow): \n Decision-Making during the COVID-19 Pandemic: Predicting Safe and Unsafe behaviors with the Corona Reflection Test
```{r RMD2, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD2_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD2_Guetzkow ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD2_Guetzkow ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD2_Guetzkow ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 3 (Caspar van Lissa): \n Cooperation, Trust, and Behavioral Responses Across Societies During the COVID-19 Pandemic
```{r RMD3, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD3_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD3_vanLissa ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD3_vanLissa ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD3_vanLissa ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 4 (Qing Han): \n Trust in government and its influence on health behaviour and prosocial behaviour during the COVID-19 pandemic
```{r RMD4, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD4_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD4_Han ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD4_Han ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD4_Han ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 5 (Anne Margit): \n Predictors of consistently high well-being during COVID-19
```{r RMD5, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD5_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD5_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD5_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD5_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 6 (Anne Margit): \n Emotional experiences across nations during COVID-19: age, gender, and cultural differences
```{r RMD6, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD6_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD6_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD6_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD6_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 7 (Anne Margit): \n The association of emotional experiences during the height of COVID-19 with well-being across nations
```{r RMD7, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD7_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD7_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD7_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD7_Margit ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 8 (Lemay): \n Hope During the COVID-19 Pandemic: Implications for Individual and National Prevention Behaviors, Infection, and Well-Being
```{r RMD8, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD8_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD8_Lemay ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD8_Lemay ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD8_Lemay ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 9 (Abakoumkin): \n Prediction of health protective behavior in the context of COVID-19 pandemic drawing from protection motivation theory
```{r RMD9, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD9_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD9_Abakoumkin ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD9_Abakoumkin ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD9_Abakoumkin ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 10 (Schumpe): \n Adoption of recommended behaviors to fight COVID-19
```{r RMD10, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD10_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD10_Schumpe ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD10_Schumpe ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD10_Schumpe ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 11 (Jin): \n Intergenerational Conflict of Interest and Prosocial Behavior During COVID-19 Pandemic
```{r RMD11, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD11_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD11_Jin ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD11_Jin ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD11_Jin ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMD 12 (Zuniga): \n Emotions, prosocial behaviour, wellbeing and disempowerment in response to the pandemic
```{r RMD12, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD12_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMD12_Zuniga ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMD12_Zuniga ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMD12_Zuniga ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```