---
title: "Psycorona - Data Sharinh"
subtitle: "Step by step description" 
author: "PsyCorona Gang"
date: "3/30/2020"
output:
  html_document: 
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
editor_options:
  chunk_output_type: console
---


<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>


```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  rm(list=ls()) # clear workspace
  gc # garbage collector
  
# Install and Load Packages
  #if(!require(pacman)) install.packages("pacman")
  # require(pacman)
  # pacman::p_load(psych, ggplot2, ggthemes, haven, data.table, dplyr, tidyr, Hmisc, mada, 
  #                knitr, kableExtra, naniar, stats, readxl, matrixStats, ISOcodes, pander,
  #                Scale)
lib <- c("psych", "ggplot2", "ggthemes", "haven", "data.table", "dplyr", "tidyr", "Hmisc", "mada", 
         "knitr", "kableExtra", "naniar", "stats", "readxl", "matrixStats", "ISOcodes", "pander", "Scale")

invisible(lapply(lib, library, character.only = TRUE))  
lapply(lib, library, character.only = TRUE)
rm(lib)  

# Load Custom Packages  
  source("./scripts/functions/fun.panel.R")
  source("./scripts/functions/themes.R")
  source("./scripts/functions/dictionary_functions.R")
  
# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(echo = TRUE)
```

Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.   

<br/>

## **Preparation**
In a first step we import the raw Qualtrics data, which was downloaded as an SPSS file.   
### Import Data
```{r LoadRawBase, echo=T, warning=F, message=F}
# Reset working directory to folder current file is saved in
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

# Import Qualtrics Survey Data
  dtClean <- read_spss("data/cleaned data/Psycorona Baseline cleaned 2020-04-20 11-42 CEST.sav")
  dtAll <- read_spss("data/cleaned data/Psycorona Baseline cleaned - All2020-04-20 11-42 CEST.sav")
  
# Import Request sheet
  dtReq <- read.csv("data/cleaned data/request/Variable Justification - Sheet1.csv", header = T)
  url <- gsheet::construct_download_url('docs.google.com/spreadsheets/d/13PFXsmgjrZBNddHodR2Z_80cjicN4s7yd8BbazKffx8/edit?usp=sharing', format = "csv", sheetid = NULL)
  dtReq <- gsheet::gsheet2tbl(url, sheetid = NULL); rm(url)
  dtReq <- dtReq[-c(1:2),]
```

### Function for Data
```{r fctExp, echo=T, warning=F, message=F}
stringOut <- NA #make var for fill out in function
nameOut <- function(df){
# if there is a B (baseline) paste the variable
  if (grepl("B",df[2], ignore.case = T)) {
    stringOut[1] = paste(df[1])
  } else {
    stringOut[1] = NA
  }
# if there is a W1 (baseline) paste w1 and the variable
  if (grepl("W1",df[2], ignore.case = T)) {
    stringOut[2] = paste("w1_", df[1], sep = "")
  } else {
    stringOut[2] = NA
  }
  if (grepl("W2",df[2], ignore.case = T)) {
    stringOut[3] = paste("w2_", df[1], sep = "")
  } else {
    stringOut[3] = NA
  }
  if (grepl("W3",df[2], ignore.case = T)) {
    stringOut[4] = paste("w3_", df[1], sep = "")
  } else {
    stringOut[4] = NA
  }
  if (grepl("W4",df[2], ignore.case = T)) {
    stringOut[5] = paste("w4_", df[1], sep = "")
  } else {
    stringOut[5] = NA
  }
  if (grepl("W5",df[2], ignore.case = T)) {
    stringOut[6] = paste("w5_", df[1], sep = "")
  } else {
    stringOut[6] = NA
  }
return(stringOut)
}
# ADD WARNING IF ZIP CODE REQUESTED
```


The raw data set includes `r length(dt0Raw)` variables for `r nrow(dt0Raw)` cases.

## **Create Datasets**
### Load in the new IDs from Excel Sheet
```{r LoadRawBase, echo=T, warning=F, message=F}
# load excell sheet
# LOAD EXCEL SHEET THAT HAS UNIQUE IDENTIFIERS (Maybe one sheet per project? How do we update new Response IDs?)  
```

### RMS 2 (Ben Guetzkow): \n Decision-Making during the COVID-19 Pandemic: Predicting Safe and Unsafe behaviors with the Corona Reflection Test
```{r RMS3, echo=T, warning=F, message=F}
# prepare dataframe
  dt <- dtAll %>%
  dplyr::select(coded_country,
            starts_with("c19ProSo"), 
            starts_with("c19perBeh"),
            starts_with("c19RCA"),
            starts_with("houseLeave"),
            -houseLeaveWhy_6_TEXT,
            -contains("_DO_"),
            -contains(".c"),
            -contains(".m"),
            -contains(".z"),
            -contains(".fa"))%>%
  dplyr::mutate_all(na_if,"")

# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMS 3 (Caspar van Lissa): \n Cooperation, Trust, and Behavioral Responses Across Societies During the COVID-19 Pandemic
```{r RMS3, echo=T, warning=F, message=F}
# prepare dataframe
  dt <- dtAll %>%
  dplyr::select(coded_country,
            starts_with("c19ProSo"), 
            starts_with("c19perBeh"),
            starts_with("c19RCA"),
            starts_with("houseLeave"),
            -houseLeaveWhy_6_TEXT,
            -contains("_DO_"),
            -contains(".c"),
            -contains(".m"),
            -contains(".z"),
            -contains(".fa"))%>%
  dplyr::mutate_all(na_if,"")

# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMS3_vanLissa_Cooperation ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMS 4 (Qing Han): \n Trust in government and its influence on health behaviour and prosocial behaviour during the COVID-19 pandemic
```{r RMS4, echo=T, warning=F, message=F}
# prepare dataframe
  dt <- dtClean %>%
             dplyr::select(starts_with("aff"),
                           starts_with("employstatus"),
                           starts_with("jbInsec"),
                           starts_with("PFS"), #financial strain
                           starts_with("fail"), #disempowerment
                           ends_with("inPerson"), #isolation in person
                           starts_with("lone"),
                           happy,
                           lifeSat,
                           C19Know,
                           c19Hope,
                           starts_with("c19ProSo"),
                           starts_with("c19perBeh"),
                           starts_with("c19Norm"),
                           starts_with("trust"),
                           extC19Msg,
                           extC19Org,
                           ecoHope,
                           starts_with("ecoProSo"),
                           starts_with("ecoProSo"),
                           starts_with("houseLeave"),
                           relYesNo,
                           whatRel,
                           coded_country,
                           countryCitizen,
                           countryCitizenIfNo,
                           Immigrant,
                           gender,
                           age,
                           edu,
                           - houseLeaveWhy_6_TEXT,
                           -contains("_DO_"),
                           -contains(".c"),
                           -contains(".m"),
                           -contains(".z"),
                           -contains(".fa"),
                           )%>%
  mutate_all(na_if,"")%>%
  mutate_all(na_if, -99)

# remove entries with "@"
  dt <- as.data.frame(lapply(dt, function(x) replace(x, grep("@", x), NA)))

# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMS4_Han_Trust ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMS4_Han_Trust ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMS4_Han_Trust ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```

### RMS 5 (Anne Margit): \n Predictors of consistently high well-being during COVID-19
```{r RMS5, echo=T, warning=F, message=F}
# prepare dataframe
  tmp <- data.frame(name = as.character(dtReq$var),
                    request = as.character(dtReq$RMD5_vars))
  tmp <- tmp %>% #remove empty rows
    dplyr::filter(request != "") 
  
# run function to get requested variable names 
  varNames <- apply(tmp, 1, nameOut); rm(tmp)

# make dataframe
  dt <- dtAll %>%
    dplyr::select(one_of(varNames),
                 -houseLeaveWhy_6_TEXT,
                 -contains("_DO_"),
                 -contains(".c"),
                 -contains(".m"),
                 -contains(".z"),
                 -contains(".fa"),
                 -contains("ZIP", ignore.case = T),
                 -ends_with("_TEXT", ignore.case = T),
                 countryCitizenIfNo)
    
# Export Dataframe
# Naming
  namSPSS <- paste0("data/collab data/RMS5_Margit_Well-Being ", format(Sys.time(), format = "%F %H-%M %Z"),".sav")
  namR <- paste0("data/collab data/RMS5_Margit_Well-Being ", format(Sys.time(), format = "%F %H-%M %Z"),".Rdata")
  namCSV <- paste0("data/collab data/RMS5_Margit_Well-Being ", format(Sys.time(), format = "%F %H-%M %Z"),".csv")
# Export
  write_sav(dt, namSPSS)
  save(dt, file = namR)
  write.csv(dt, file = namCSV)
rm(dt, namSPSS, namR, namCSV)
```